---
title: Developing Data Products Week 2 Assignment by John Hopkins University through
  Coursera
author: "Niño Lito Jake Briones"
date: "August 20, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## INSTRUCTION:
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## CRITERIA:
The rubric contains the following two questions:

1.Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?


2. Does the web page feature an interactive map that appears to have been created with Leaflet?

## SUBMISSION:

I created a pop up map of my hometown here in the Philippines.

```{r}
library(leaflet)

Laguna <- leaflet() %>%
  addTiles() %>%
addMarkers(lat=14.0642, lng=121.3233, popup = "My Hometown")

Laguna
```


